### 2019-02-27 sections/example.tex
typo in example

The function \TS{confirmBooking} removes the picked seats from the shared list of free seats,
and displays the end result using an editor, depicted by \TS{edit}.
\begin{TASK}
  let confirmBooking = \ps. \ss.
    freeSeats := difference !freeSeats ss; edit <<ps, ss>>
\end{TASK}
% It uses a function \TS{difference}, which removes all elements from the second list from the first list.

>>>>

The function \TS{confirmBooking} removes the picked seats from the shared list of free seats,
and displays the end result using an editor, denoted by \TS{edit}.
\begin{TASK}
  let confirmBooking = \ps. \ss.
    freeSeats := difference !freeSeats ss; edit <<ps, ss>>
\end{TASK}
% It uses a function \TS{difference}, which removes all elements from the second list from the first list.
